New results in $\sfrac{k}{n}$ Power-Hours

### 2013-12-28 powerhour/paper/paper.tex
Add composite placeholder
Made thing that can plot sampled grids. Made powerhour properly honor symmetry when filling in the grid, at least

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{3and2.pdf}
\end{center}\vspace{-0.1in}
\caption{Outcomes possible for the first two players in all different
  3-player power hours (black), overlayed by all possible outcomes
  outcomes for 2-player power hours (red). Mainly included because
  it looks pretty sweet.
}
\label{fig:3and2}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{powerday3.pdf}
\end{center}\vspace{-0.1in}
\caption{All possible outcomes for the first two players in 3-player
  power days. These are the same games as the 3-player power hours,
  but at this scale makes it clear the groupings and their sparsity
  in the limit. Lines plotted from (0,0) to (60,*) and (*,60) show
  significant structure, but don't explain some of the interior points.
  (TODO: what are these games? what did the other player drink?)
}
\label{fig:powerday3}
\end{figure}

@@

@@

@@

Define BMnL, where $n$ is the number of non-filled states. BMML=BM2L.
Find $n$ such that a solo or dual power hour achieves any $k$.

>>>>

% XXX TODO: Display in 3D cube.
It is also feasible overnight to enumerate all three-player games. The
results are three-dimensional, of course, but we can display the
outcomes for two of the players in the familiar presentation
(Figure~\ref{cig:3and2}). Note that $\langle k_1, k_2, k_3 \rangle$ is
achievable for any $k_1$, $k_2 \in \{ 0, 1, 2 \}$, and some unknown
$k_3$ (projected out of this display). This is a significant
improvement over what was achievable in BMML with two players. It
suggests that with enough friends willing to follow a program, some
set of people are likely to be able to achieve any amount of drinks
between them (if they have the ability to construct the right rule
set!); see Section~\ref{sec:conjectures}.

The sheer number of configurations for 4 or more players makes these
exact enumeration techniques infeasible. However, we have other
avenues for generalization (and exploration), which are explored in
the next chapter.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{3and2.pdf}
\end{center}\vspace{-0.1in}
\caption{Outcomes possible for the first two players in all different
  3-player power hours (black), overlayed by all possible outcomes
  outcomes for 2-player power hours (red). Mainly included because
  it looks pretty sweet. The outcomes that are possible with three
  players are a superset of those with two, which is intuitive: We
  can add a third player to any game who just does nothing.}
\label{fig:3and2}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{powerday3.pdf}
\end{center}\vspace{-0.1in}
\caption{All possible outcomes for the first two players in 3-player
  power days. These are the same games as the 3-player power hours,
  but at this scale makes it clear the groupings and their sparsity
  in the limit. Lines plotted from (0,0) to (60,*) and (*,60) show
  significant structure, but don't explain some of the interior points.
  (TODO: what are these games? what did the other player drink?)
  (TODO: Incorporate this into the text, perhaps after discussing
  the linear combination trick.)
}
\label{fig:powerday3}
\end{figure}

@@

Like any drinking game, there are several arbitrary things about BMML.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.90 \linewidth]{composite2playermock.png}
\end{center}\vspace{-0.1in}
\caption{What's achievable for the first two players in a three-player
  generalized BM$n$L game, with $n$ ranging from 1 cup state (darkest)
  to 5 (lightest). TODO WRITEME
% 6 cupstates ran overnight and got here:
% #26186200000 queue 109 min 49 466729 states/sec 796272 config/sec
}
\label{fig:composite2player}
\end{figure}

\section{Samping games}

@@

Define BMnL, where $n$ is the number of non-filled states. BMML=BM2L.
(XXX actually I think it's the total number of states including filled
everywhere but that sentence, right?)  Find $n$ such that a solo or
dual power hour achieves any $k$.

\begin{enumerate}
  \item With one player, we have exact bounds on what is possible in
    the generalized case. With 8 cup states, a single player can
    drink 0--60 shots. Since each player can just play independently,
    this result extends to any number of players in BM8L.
  \item With two players, we know that BM5L (XXX check) does not allow
    all combinations of $\langle k_1, k_2 \rangle$ shots, though BM5L
    can achieve any $\langle k_1, k_2 \rangle$ where $\k_2 \in \{ 0, 1
    \}$. No other $k_2$ can be used universally, though of course many
    other combinations are possible
    (Figure~\ref{fig:compositeplayer2mock}).
  \item Open: Can BM6L achieve all $\langle k_1, k_2 \rangle$? Seems
    unlikely, based on how many samples we need to get close to 100\%
    for BM7L.
  \item Open: Can BM7L achieve all $\langle k_1, k_2 \rangle$? Seems
    likely, given how close BM7L is for a single player. We know it
    can get 96.67\%, at least!
  \item With three players one player can drink any number of shots in
    BMML with two other players helping.
\end{enumerate}
